Learning and Recognition of \strips\ Action Models from State Observations \\ Action Model Recognition from State Observations via Planning

### 2018-01-22 doc/ijcai-18/observations-learning.tex
Add files via upload

This paper presents a first novel approach to \strips\ action model recognition from state observations. Unlike other related works, our classical planning compilation approach not only allows learning a \strips\ action model from an observation sequence but it is also extendible to action model recognition. The learning task does not require observing the precise actions that produce the state observations because such actions are determined by a classical planner. We present a two-fold evaluation of the learned models: a syntactic and semantic assessment against a reference model and via a test dataset that calculates the probability of a model given the observation. Moreover, we show how these probabilistic values are used to estimate the probability of the action model recognition.

>>>>

This paper presents a first novel approach to \strips\ action model recognition from state observations. Unlike other related works, our classical planning compilation approach learns a \strips\ action model from state observations instead of action observations and it is also extendible to action model recognition. We present a two-fold evaluation of the learned models: a syntactic and semantic assessment against a reference model and calculating the probability of the model given the observations with a test dataset. Moreover, we show how these probabilistic values are used to estimate the probability of the action model recognition.
